---
title: "BTM Implementation"
output: html_notebook
---

Using [BTM cran package](https://cran.r-project.org/web/packages/BTM/BTM.pdf), based on [this](https://github.com/bnosac/BTM) GitHub code.

```{r}
library(tidytext)
library(dplyr)
library(udpipe)
library(BTM) # topic modelling
library(data.table) # dataframe to datatable

# visualise model
library(textplot)
library(ggraph)
library(concaveman)
library(igraph)
library(ggforce)
```

```{r}
RUN_LOGLIK <- FALSE # set this to true if you want to run the loglik code again
```

```{r}
df <- read.csv("../datain/topic_modelling/cleaned_tweets_largest_community_btm.csv")
df
```
```{r}
clean_tweets <- function(tweets_in) {
  # unnest tokens
  tidy_tweets <- tweets_in %>% 
    unnest_tokens(word, cleaned_tweet, token = "tweets")

  return(tidy_tweets)
}

df <- clean_tweets(df)
```


data: a tokenised data frame containing one row per token with 2 columns

* the first column is a context identifier (e.g. a tweet id, a document id, a sentence id, an identifier of a survey answer, an identifier of a part of a text)

* the second column is a column called of type character containing the sequence of words occurring within the context identifier

```{r convert data frame to data table (set)}
# https://stackoverflow.com/questions/48758883/r-dataset-not-found
setDT(df)
df
```

```{r set BTM parameters}
numTopics <- 11 # optimal number of topics for sample data
numGibbsIter <- 1000 # can adjust to be lower for faster run time (but less accuracy)
gibbsEvolution <- 100 # can adjust to be lower for faster run time (but less accuracy)
```

```{r run BTM model}
set.seed(1234)
model <- BTM(data = df, k = numTopics, iter = numGibbsIter, trace = gibbsEvolution)
```

```{r get most optimal topic numbers (BTM LogLik values)}
if (RUN_LOGLIK) {
  fit <- logLik(model)
  fit$ll
}
```

```{r the probability of terms being in a particular topic}
topicterms <- terms(model, top_n = 20)
topicterms
```

```{r matrix with the probabilities of each tweet being associated with a particular topic}
scores <- predict(model, newdata = df)
scores
```

# Plot
```{r plot default}
plot(model)
```

```{r plot all topics with labels}
# https://rdrr.io/cran/textplot/man/plot.BTM.html

plot(model, labels = 1:model$K)
```

```{r}
ggplot_build.ggplot()
```

```{r plot topic 11 (the largest topic)}
plot(model, which = 11, top_n = 20, title="Topic 11")
```

## Save plots
```{r save as vector/pdf with labels}
# Step 1: Call the pdf command to start the plot
pdf(file = "dataout/model_11_labels_blanktitle.pdf", # The directory you want to save the file in
    width = 15, # The width of the plot in inches
    height = 9) # The height of the plot in inches

# Step 2: Create the plot with R code
plot(model, labels = 1:model$K, title="")

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r save as vector/pdf without labels}
# Step 1: Call the pdf command to start the plot
pdf(file = "dataout/model_11.pdf",   # The directory you want to save the file in
    width = 15, # The width of the plot in inches
    height = 9) # The height of the plot in inches

# Step 2: Create the plot with R code
plot(model, title="") 

# Step 3: Run dev.off() to create the file!
dev.off()
```

```{r save topic 11 as vector/pdf with labels}
# Step 1: Call the pdf command to start the plot
pdf(file = "dataout/model_11_alone_10terms.pdf",   # The directory you want to save the file in
    width = 3, # The width of the plot in inches
    height = 2.7) # The height of the plot in inches

# Step 2: Create the plot with R code
plot(model, which = 11, top_n = 10, title="Topic 11")

# Step 3: Run dev.off() to create the file!
dev.off()
```


# Write results to files
```{r write results to files}
# create output directory if it doesn't exist
dir.create("data", showWarnings = FALSE)
# a matrix containing containing P(z|d) - the probability of the topic given the biterms.
# The matrix has one row for each unique doc_id (context identifier) which contains words part of the dictionary of the BTM model and has K columns, one for each topic.
write.csv(x=scores, file=sprintf("data/%d_model_scores.csv", numTopics))
```








